\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-14 docs/paper.tex
Change to present tense

\abstract{
The introduction of Internationalized Domain Names (IDNs) made access the web easier to non-English speakers.
However, it also opened up the possibility of using homograph domain names maliciously, in what has been called IDN homograph attacks.
This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
Our approach to analyze its potential impact was based on clustering IDNs with their canonical counterparts in the Alexa Top 1m web sites ranking.
The results obtained indicate that there are more than a thousand IDN homographs among \textit{.com} domains.
While most of them are not being used actively, they still possess a potential security risk as there are no guarantees they will remain inactive in the future.
}

@@

All major browsers display the URL in Punycode instead of Unicode if certain conditions are met, to defend the user against a possible IDN homograph attack.
The specific conditions, however, are different for each browser.
Figure~\ref{screenshot-apple} shows a successful attack where the homograph domain name was not detected.
Figure~\ref{screenshot-google} show an unsuccessful attack, where the URL is displayed in Punycode.

@@

In 2012, Maurer and H\"{o}fer argued that safe-guards based on browsers' blacklists was far from enough to protect users from sophisticated phishing attacks~\cite{maurer2012}.
They proposed a more complex method based on URL components and the spell checking functionality of any search engine.
In this method, a URL is be divided into several parts, namely, base name (the primary domain name as registered at the registrar), sub-domain (part before the primary domain, i.e., before the last identifier and TLD), path domain (sub-folder of the URL), and brand name (any popular brand name that is present in the URL).
Their algorithm tries to prevent the attack by analyzing each of these URL parts.
Each one is sent to the search engine for a spell check, and in the cases that a spelling suggestion is returned, the URL will be marked as suspicious.
By splitting the URL into these parts, this method aims to cover almost all possible cases of confusable URLs or domain names.
However, this mechanism relies exclusively on the search engine to return spelling suggestions, resulting in its highly dependence on the search engine and query itself.

@@

Our approach to analyze the potential security risk of homograph IDNs was fundamentally different the ones evaluated.
Rather than inspecting traffic or generating random homograph permutations of a string, we took a more systematic approach.
We clustered all internationalized homograph domains using a snapshot of the \texttt{.com} domain zone.
We then used a list of top web sites and domain registrants data to classify each homograph domain name.

\section{Methodology}
Our data collection involved two primary sources.
The first one was a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
This snapshot was provided by Verisign\endnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
It contains, for the most part, the name servers of all \texttt{.com} and \texttt{.net} domains.
For the purposes of this project, only the \texttt{.com} domains were considered.

The second data source was the \textit{Alexa Top 1 million sites ranking}\endnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
It contains the most popular one million web sites (as ranked by Alexa), regardless whether they are \texttt{.com} domains or not.
It was also retrieved on 2017/05/01.

@@

\subsection{Data Processing}
We used the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
All IDNs are represented using Punycode, so they start with the \texttt{xn--} prefix.
Using this information we first filtered the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
Since the \textit{.com snapshot} contains name server records, a single domain may have more than one entry in the file.
Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} were discarded.
We sorted the domains in lexicographical order, removing duplicates in the process.

We used the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
As we were only interested in non-IDNs, we discarded the ones that start with the prefix \texttt{xn--}.
We also removed sub-domains, since we only had second level domain names in the \textit{.com snapshot}.

\subsection{Clustering}
The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
To detect potential internationalized domain name homograph attacks, we clustered the IDNs in the \textit{.com snapshot}.
The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we called canonical domain name.
Only clusters with at least one internationalized homograph domain name were output.

The detection of homograph domain names was done using an algorithm to check if two strings are confusable.
This algorithm is described in the \textit{Unicode Technical Standard \#39}.
The approach followed has some caveats, that could be addressed in future work.
For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking Unicode character.
More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top-level domains following the same procedure.
All things considered, we still think this approach is a valuable first step.

Another type of clustering was also performed.
We grouped the homograph domain names by its registrant organization, and ranked each organization by the number of homograph domain names to their name.
This could shed light on which registrant organizations are allowing homograph domain names, or even on which individuals and companies are doing it the most.

@@

\subsection{Manual Classification}
The last part of the data processing was the classification of the homograph domain names.
This classification was done manually, to be able to differentiate between scam and unrelated websites.
To help with the classification and speed up the process, we queried the \textit{WHOIS} records\endnote{\url{https://whois.icann.org}} of every homograph domain name.
Some domains had expired at the time of the classification, and were subsequently deleted from the output file.

The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
The first one, \textit{Canonical}, was employed when the domain is registered by the same organization as its canonical homograph domain name.
The second one, \textit{Third Party}, was used when the domain is registered by a different organization than its canonical homograph domain name.
Additionally, a more detailed classification was made:
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item \textit{Canonical - Parking}: domain was registered but it was not accessible via HTTP.
\item \textit{Canonical - Redirect}: domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Redirect to Canonical:} domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Unrelated}: domain resolved, but the contents of the website were totally unrelated to its canonical homograph domain name.
\item \textit{Third Party - Parking}: domain was registered, but it was not accessible via HTTP, or when accessed, a default domain parking web page was displayed.
\item \textit{Third Party - Scam}: domain resolved, and the website displayed was a clear attempt (similar color, logos, etc.) to make users think they were visiting the canonical homograph domain name.
\end{itemize}

\section{Results}
We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
However, only a low percentage of the IDNs (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of IDNs are not being used in homograph attacks.
An overview of these clustering results can be found in Table~\ref{clustering-results}.

@@

\section{Ethical Considerations}
The domain information used in this project is publicly available, and was voluntarily provided by the registrants of the domains when they registered them.
The full \texttt{.com} domain zone snapshot will not be publicly disclosed, as its access requires a paid subscription.
The retrieval of the \textit{WHOIS} information was performed only for the homograph IDNs, which were about one thousand.
It was performed with a significant delay between petitions (3 seconds) in order to avoid saturating the servers.

>>>>

\abstract{
The introduction of Internationalized Domain Names (IDNs) made access the web easier to non-English speakers.
However, it also opened up the possibility of using homograph domain names maliciously, in what has been called IDN homograph attacks.
This kind of attack can be used to trick users into thinking they are visiting a different (but homograph) domain name.
Our approach to analyze its potential impact is based on clustering IDNs with their canonical counterparts in the Alexa Top 1 million web sites ranking.
The results obtained indicate that there are more than a thousand IDN homographs among \textit{.com} domains.
While most of them are not being used actively, they still possess a potential security risk as there are no guarantees they will remain inactive in the future.
}

@@

All major browsers display the URL in Punycode instead of Unicode if certain conditions are met, to defend the user against a possible IDN homograph attack.
The specific conditions, however, are different for each browser.
Figure~\ref{screenshot-apple} shows a successful attack where the homograph domain name is not detected.
Figure~\ref{screenshot-google} show an unsuccessful attack, where the URL is displayed in Punycode.

@@

In 2012, Maurer and H\"{o}fer argued that safe-guards based on browsers' blacklists was far from enough to protect users from sophisticated phishing attacks~\cite{maurer2012}.
They proposed a more complex method based on URL components and the spell checking functionality of any search engine.
In this method, a URL is divided into several parts, namely, base name (the primary domain name as registered at the registrar), sub-domain (part before the primary domain, i.e., before the last identifier and TLD), path domain (sub-folder of the URL), and brand name (any popular brand name that is present in the URL).
Their algorithm tries to prevent the attack by analyzing each of these URL parts.
Each one is sent to the search engine for a spell check, and in the cases that a spelling suggestion is returned, the URL will be marked as suspicious.
By splitting the URL into these parts, this method aims to cover almost all possible cases of confusable URLs or domain names.
However, this mechanism relies exclusively on the search engine to return spelling suggestions, resulting in its highly dependence on the search engine and query itself.

@@

Our approach to analyze the potential security risk of homograph IDNs is fundamentally different from the ones evaluated.
Rather than inspecting traffic or generating random homograph permutations of a string, we take a more systematic approach.
We cluster all internationalized homograph domains using a snapshot of the \texttt{.com} domain zone.
We then use a list of top web sites and domain registrants data to classify each homograph domain name.

\section{Methodology}
Our data collection involves two primary sources.
The first one is a snapshot of the \texttt{.com} and \texttt{.net} domain zone, from now on referenced as \textit{.com snapshot}.
This snapshot has been provided by Verisign\endnote{\url{https://www.verisign.com/en_US/channel-resources/domain-registry-products/zone-file/index.xhtml}}, and it is dated on 2017/05/01.
It contains, for the most part, the name servers of all \texttt{.com} and \texttt{.net} domains.
For the purposes of this project, only the \texttt{.com} domains have been considered.

The second data source is the \textit{Alexa Top 1 million sites ranking}\endnote{\url{https://www.alexa.com/topsites}}, from now on referenced as \textit{top domains snapshot}.
It contains the most popular one million web sites (as ranked by Alexa), regardless whether they are \texttt{.com} domains or not.
It was also retrieved on 2017/05/01.

@@

\subsection{Data Processing}
We use the \textit{.com snapshot} to obtain all the internationalized domains of the \texttt{.com} domain zone.
All IDNs are represented using Punycode, so they start with the \texttt{xn--} prefix.
Using this information we first filter the \textit{.com snapshot} to match only the \texttt{.com} domains that start with \texttt{xn--}.
Since the \textit{.com snapshot} contains name server records, a single domain may have more than one entry in the file.
Only the domain name is relevant for this project, so the rest of the columns of the \textit{.com snapshot} can be discarded.
We sort the domains in lexicographical order, removing duplicates in the process.

We use the \textit{top domains snapshot} as a source for the canonical (non-international) domain name of a website, based on its ranking.
As we are only interested in non-IDNs, we can discard the ones that start with the prefix \texttt{xn--}.
We also remove sub-domains, since we only have second level domain names in the \textit{.com snapshot}.

\subsection{Clustering}
The underlying assumptions behind the clustering process are that homograph attacks are more likely to target popular domains, and that the million domains from the \textit{top domains snapshot} contains most of the popular domains.
To detect potential internationalized domain name homograph attacks, we cluster the IDNs in the \textit{.com snapshot}.
The representative of each cluster is a homograph domain name from the \textit{top domains snapshot}, which we call canonical domain name.
Only clusters with at least one internationalized homograph domain name are output.

The detection of homograph domain names is done using an algorithm to check if two strings are confusable.
This algorithm is described in the \textit{Unicode Technical Standard \#39}.
The approach followed has some caveats, that could be addressed in future work.
For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking Unicode character.
More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
It is also worth noting that only domain names from the \texttt{.com} zone are considered, but similar studies could be done to other top-level domains following the same procedure.
All things considered, we still think this approach is a valuable first step.

Another type of clustering is also performed.
We group the homograph domain names by its registrant organization, and rank each organization by the number of homograph domain names to their name.
This could shed light on which registrant organizations are allowing homograph domain names, or even on which individuals and companies are doing it the most.

@@

\subsection{Manual Classification}
The last part of the data processing is the classification of the homograph domain names.
This classification is done manually, to be able to differentiate between scam and unrelated websites.
To help with the classification and speed up the process, we query the \textit{WHOIS} records\endnote{\url{https://whois.icann.org}} of every homograph domain name.
Some domains are expired at the time of the classification, and are subsequently deleted from the output file.

The two high level categories defined are \textit{Canonical} and \textit{Third Party}.
The first one, \textit{Canonical}, is employed when the domain is registered by the same organization as its canonical homograph domain name.
The second one, \textit{Third Party}, is used when the domain is registered by a different organization than its canonical homograph domain name.
Additionally, a more detailed classification is made:
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item \textit{Canonical - Parking}: domain is registered but it is not accessible via HTTP.
\item \textit{Canonical - Redirect}: domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Redirect to Canonical:} domain redirects (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Unrelated}: domain resolves, but the contents of the website are totally unrelated to its canonical homograph domain name.
\item \textit{Third Party - Parking}: domain is registered, but it is not accessible via HTTP, or when accessed, a default domain parking web page is displayed.
\item \textit{Third Party - Scam}: domain resolves, and the website displayed is a clear attempt (similar color, logos, etc.) to make users think they are visiting the canonical homograph domain name.
\end{itemize}

\section{Results}
We obtain 458731 domain names from the \textit{top domains snapshot} that belong to the \texttt{.com} zone.
From the \textit{.com snapshot}, we identify a total of 1044301 internationalized domains.
However, only a low percentage of the IDNs (3.68\%) have a matching homograph canonical domain name in the \textit{top domains snapshot}.
Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of IDNs are not being used in homograph attacks.
An overview of these clustering results can be found in Table~\ref{clustering-results}.

@@

\section{Ethical Considerations}
The domain information we use in this project is publicly available, and is voluntarily provided by the registrants of the domains when they register them.
The full \texttt{.com} domain zone snapshot will not be publicly disclosed, as its access requires a paid subscription.
The retrieval of the \textit{WHOIS} information is done only for the homograph IDNs, which are about one thousand.
It is performed with a significant delay between petitions (3 seconds) in order to avoid saturating the servers.
